Example and Tutorial for Vim Editor (Linux)

### 2020-01-10 nontex/install/linux/fn_vim.Rmd
vim delete and insert, D

@@

- delete current word and go into insert mode: *ciw*
- Delete current word: *dw*
- Delete from cursor until end of sentence: *dis*
- Delete from cursor to end of line: *d$* or *D*
- Delete until end of paragraph: *dip*
- Delete all text in file: *ggdG*

@@

- Copy current word: *dw*
- Copy from cursor to end of line (need to set this): *y$* or *Y*
- Copy until end of paragraph: *yip*

>>>>

**Delete and Insert**:

- delete from now till end of sentence and insert mode: *C*
- delete whole sentence you are on and insert: *cc*
- delete until end of sentence and insert mode: *cis*
- delete current word and go into insert mode: *cw*

@@

- Delete current word: *dw*
- Delete from cursor until end of sentence: *dis*
- Delete from cursor to end of line: *d$* or *D*
- Delete until end of paragraph: *dip*
- Delete all text in file: *ggdG*

@@

- Copy current word: *dw*
- Copy from cursor to end of line (need to set this): *y$* or *Y*
- Copy until end of paragraph: *yip*
- Copy all text on page: *ggVGY*
